---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geodato

<!-- badges: start -->

<!-- badges: end -->

An R package to hold and facilitate geographies for spatial analysis.

## Installation

You can install the development version of geodato from [GitHub](https://github.com/) with:

```r
install.packages("devtools")
devtools::install_github("datasketch/geodato")
```

## Available maps

The available maps inside the package can be checked by running `available_maps_df()`:

```{r}
library(geodato)

available_maps_df
```

## Getting a map from geodato
```{r}
library(geodato)
library(ggplot2)

tj <- geodato::gd_tj("col_municipalities")

ggplot(tj) +
  geom_sf(fill = "#CCCCCC", color= "#444444") +
  theme_void()
```


## How to contribute

A new map can be added by following the steps described on the article `new-geography-layer`, available by running `vignette("new-geography-layer.Rmd")`
